Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-07 doc/JFLA2022/paper.tex
improve (?) introduction of Section 2

 In mathematical terms, if at step $n$ the hydra is associated with the ordinal $\alpha$, at step $n+1$ it is associated with
 $\canonseq{\alpha}{n+1}$, \emph{i.e.} the $(n+1)$th element of the canonical sequence of $\alpha$~\cite{KS81}.

>>>>

 In mathematical terms, if at step $n\geq i$, the hydra is associated with the ordinal $\alpha$, at step $n+1$ it is associated with
 $\canonseq{\alpha}{n+1}$, \emph{i.e.} the $(n+1)$th element of the canonical sequence of $\alpha$~\cite{KS81}.
